A graph-based approach for interactive evolutionary computation

### 2017-01-17 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Intro

\section{Introduction}
Interactive Evolutionary Algorithms (IEAs): are standard EAs whose
fitness evaluations are performed by persons with in an interactive 
system.  Thus, the main loop of the EA needs the intervention of a
human for the quality assessment of each proposed solution. These
systems have an inherent drawback araising from the very nature of 
the algorithm, namely, the human fatigue caused by the interaction. 
Some authors have already tried to address this basic problem \cite{Frade:2010:EvoGAMES}.
nevertheless, IEAs have demonstrated their ability for effectively
producing art and design \cite{Bentley:1999:intro,Sims:1991,todd:1992},
as well as other products in many other domains \cite{ie1}. 
Several IEC have been developed as web based systems \cite{picbreeder,Musart},
depending on volunteers who visit the system to interactibly help
with the seach.

>>>>

\section{Introduction}
Interactive Evolutionary Algorithms (IEAs): are standard EAs whose
fitness evaluations are performed by persons with in an interactive 
system.  Thus, the main loop of the EA needs the intervention of a
human for the quality assessment of each proposed solution. These
systems have an inherent drawback araising from the very nature of 
the algorithm, namely, the human fatigue caused by the interaction. 
Some authors have already tried to address this basic problem \cite{Frade:2010:EvoGAMES}.
nevertheless, IEAs have demonstrated their ability for effectively
producing art and design \cite{Bentley:1999:intro,Sims:1991,todd:1992},
as well as other products in many other domains \cite{ie1}. 
Several IEC have been developed as web based systems \cite{picbreeder},
who depend on volunteers who visit the system to interactively help
with the search, using both anonymous and registered users. In particular
the EvoSpace-Interactive (ES-I) platform employs a collaborative technique,
where several registered users assign a quality assessment to a single
individual and then an aggregated fitness value is calculated. The fitness
assigned to each individual depends on the taste of each particular user, 
resulting in a many-to-many relationship between users and individuals. 
Many systems query this user-individual relation to extract relevant
knowledge about the process and the population, for instance showing the
most popular individual, or the the user with more participation \cite{picbreeder}.
In order to do this, individuals about individuals must be stored, even
if they are no longer in the active population. In this work a graph database
is proposed to model the interaction between users and individuals, with
the following considerations:

\begin{enumerate}
  \item  The relationship between individuals is naturally expressed as a
  tree, or a graph when both ancestors and descendancy is considered.

  \item Relationship between users can also be modeled as a social network,
  with well stablished algorithms and metrics (cite).

  \item Fitness evaluation can also be extracted from different kind of relationships
  between a user and an individual, using common actions? found in social networks,
  for instance share, like, or add to collection.

\end{enumerate}
